---
title: "Hospitalization scenarios"
author: "Michael Garber"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
#Load data and packages
library(here)
library(mapview)
library(tidyverse)
library(viridis)
library(viridisLite)
setwd(here("data-processed"))
load("hosp_both_geo.RData")
#Data created here:
#heat-hosp-california/scripts/link-zcta-hosp-data.R
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
#Define mapview functions

mv_ratio_fun = function(var_name){
  hosp_both_geo %>% 
    filter(ratio_diff=="ratio") %>% 
    dplyr::select("zcta", all_of(var_name), "ratio_diff") %>% 
    mapview(
      col.regions= viridis_pal(option = "A", direction = 1),
      zcol = var_name,
      basemaps = c("CartoDB.Positron", "CartoDB.DarkMatter"),
      layer.name = "Ratio")
}

mv_diff_fun = function(var_name){
  hosp_both_geo %>% 
    filter(ratio_diff=="diff") %>% 
    dplyr::select("zcta", all_of(var_name), "ratio_diff") %>% 
    mapview(
      col.regions= viridis_pal(option = "D", direction = 1),
      zcol = var_name,
      basemaps = c("CartoDB.Positron", "CartoDB.DarkMatter"),
      layer.name = "Difference")
}

```

# Scenario definitions

-   Tree canopy

    -   Population-based Scenario: AI: Increase by 10% in all zip codes

    -   Targeted

        -   Scenario AII1: Increase by 10% in zip codes in the lowest 1/5th of current TC cover (i.e. \<=20th pctile)

        -   Scenario AII2: Increase by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. \>80th pctile)

        -   Scenario AII3: Increase by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. \>80th pctile)

    -   Proportionate-universalism

        -   Scenario AIII1: Increase by 10% for bottom 1/5th of current TC cover... down to 2% for top 1/5th

        -   Scenario AIII2: Increase by 10% for top 1/5th of SVI ... down to 2% for bottom 1/5th

        -   Scenario AIII3: Increase by 10% for top 1/5th of hospitalization burden ... down to 2% for bottom 1/5th

-   Impervious surface cover

    -   Population-based: Scenario BI: Decrease by 10% in all zip codes

    -   Targeted

        -   Scenario BII1: Decrease by 10% in zip codes in the highest 1/5th of current imperv cover (i.e. \>80th pctile)

        -   Scenario BII2: Decrease by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. \>80th pctile)

        -   Scenario BII3: Decrease by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. \>80th pctile)

    -   Proportionate-universalism

        -   Scenario BIII1: Decrease by 10% for top 1/5th of current imperv cover ... down to 2% for bottom 1/5th

        -   Scenario BIII2: Decrease by 10% for top 1/5th of SVI ... down to 2% for bottom 1/5th

        -   Scenario BIII3: Decrease by 10% for top 1/5th of hospitalization burden ... down to 2% for bottom 1/5th



# Visualization of scenarios
The following maps visualize, for each scenario, ratio-based and difference-based effect estimates on hospitalizations in California at the level of the zip-code tabulation area.

## Tree canopy
### Population-based Scenario
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AI")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AI")
```

### Targeted Scenario
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AII1")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AII1")
```

