---
title: "Hospitalization scenarios"
#author: "Michael Garber"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
#Load data and packages
library(here)
library(mapview)
library(tidyverse)
library(viridis)
library(viridisLite)
library(leaflet)
library(leaflet.extras)
setwd(here("data-processed"))
load("hosp_both_geo.RData")
#Data created here:
#heat-hosp-california/scripts/link-zcta-hosp-data.R
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
#Define mapview functions

#Set basemaps
mapviewOptions(
  basemaps = c("CartoDB.Positron","CartoDB.DarkMatter"))
mv_ratio_fun = function(var_name){
  hosp_both_geo %>% 
    filter(ratio_diff=="ratio") %>% 
    dplyr::select("zcta", all_of(var_name), "ratio_diff") %>% 
    mapview(
      col.regions= viridis_pal(option = "A", direction = 1),
      zcol = var_name,
     lwd=.75,
      layer.name = "Ratio")
}

mv_diff_fun = function(var_name){
  hosp_both_geo %>% 
    filter(ratio_diff=="diff") %>% 
    dplyr::select("zcta", all_of(var_name), "ratio_diff") %>% 
    mapview(
      col.regions= viridis_pal(option = "D", direction = 1),
      zcol = var_name,
      lwd=.75,
      layer.name = "Difference")
}

```

# Scenario definitions

-   Tree canopy

    -   Population-based Scenario: AI: Increase by 10% in all zip codes

    -   Targeted

        -   Scenario AII1: Increase by 10% in zip codes in the lowest 1/5th of current TC cover (i.e. \<=20th pctile)

        -   Scenario AII2: Increase by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. \>80th pctile)

        -   Scenario AII3: Increase by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. \>80th pctile)

    -   Proportionate-universalism

        -   Scenario AIII1: Increase by 10% for bottom 1/5th of current TC cover... down to 2% for top 1/5th

        -   Scenario AIII2: Increase by 10% for top 1/5th of SVI ... down to 2% for bottom 1/5th

        -   Scenario AIII3: Increase by 10% for top 1/5th of hospitalization burden ... down to 2% for bottom 1/5th

-   Impervious surface cover

    -   Population-based: Scenario BI: Decrease by 10% in all zip codes

    -   Targeted

        -   Scenario BII1: Decrease by 10% in zip codes in the highest 1/5th of current imperv cover (i.e. \>80th pctile)

        -   Scenario BII2: Decrease by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. \>80th pctile)

        -   Scenario BII3: Decrease by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. \>80th pctile)

    -   Proportionate-universalism

        -   Scenario BIII1: Decrease by 10% for top 1/5th of current imperv cover ... down to 2% for bottom 1/5th

        -   Scenario BIII2: Decrease by 10% for top 1/5th of SVI ... down to 2% for bottom 1/5th

        -   Scenario BIII3: Decrease by 10% for top 1/5th of hospitalization burden ... down to 2% for bottom 1/5th



# Visualization of scenarios
The following maps visualize, for each scenario, ratio-based and difference-based effect estimates on hospitalizations in California at the level of the zip-code tabulation area.


## Tree canopy
### Population-based Scenario: Increase by 10% in all zip codes
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AI")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv = mv_diff_fun("AI")
mv@map %>% 
  addFullscreenControl()
```

### Targeted Scenarios
#### Scenario AII1: Increase by 10% in zip codes in the lowest 1/5th of current TC cover (i.e. <=20th pctile) 
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AII1")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AII1")
```

#### Scenario AII2: Increase by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. >80th pctile)
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AII2")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AII2")
```

#### Scenario AII3: Increase by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. >80th pctile)
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AII3")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AII3")
```

### Proportinate-universalism Scenarios
#### Scenario AIII1: Increase by 10% for bottom 1/5th of current TC cover… down to 2% for top 1/5th
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AIII1")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AIII1")
```

#### Scenario AIII2: Increase by 10% for top 1/5th of SVI … down to 2% for bottom 1/5th
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AIII2")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AIII2")
```

#### Scenario AIII3: Increase by 10% for top 1/5th of hospitalization burden … down to 2% for bottom 1/5th
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("AIII3")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_diff_fun("AIII3")
```

## Impervious surface cover
### Population-based Scenario: Decrease by 10% in all zip codes
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BI")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BI")
```

### Targeted Scenarios
#### Scenario BII1: Decrease by 10% in zip codes in the highest 1/5th of current imperv cover (i.e. >80th pctile)
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BII1")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BII1")
```

#### Scenario BII2: Decrease by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. >80th pctile)
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BII2")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BII2")
```

#### Scenario BII3: Decrease by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. >80th pctile)
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BII3")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BII3")
```

### Proportionate-universalism
#### Scenario BIII1: Decrease by 10% for top 1/5th of current imperv cover … down to 2% for bottom 1/5th
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BIII1")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BIII1")
```


#### Scenario BIII2: Decrease by 10% for top 1/5th of SVI … down to 2% for bottom 1/5th 
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BIII2")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BIII2")
```

#### Scenario BIII3: Decrease by 10% for top 1/5th of hospitalization burden … down to 2% for bottom 1/5th
Ratio
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BIII3")
```

Difference
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
mv_ratio_fun("BIII3")
```
