---
title: "Static maps"
author: "Michael D Garber"
date: "`r Sys.Date()`"
output: html_document
---

Copied from heat-hosp-california/docs/vis-definitions-plots.Rmd
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
library(readxl)
library(here)
library(tidyverse)
library(viridis)
library(sf)
source(here("scripts","read-attrib-hosps-ratios-diffs.R"))#load measures
setwd(here("data-processed"))
load("zcta_ca_geo_simplified.RData")
```

# Static maps
Ideas for static maps of measures using facet plots
## IRR

### Population-based scenarios: Impervious surfaces vs. Tree canopy
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
ggplot_facet_pb_imp_v_tree=function(df,measure_value, direction_value){
  df %>% 
  ggplot()+
  geom_sf(
    aes(fill=value_cat),
    linewidth=.05)+
  scale_fill_viridis(
    direction=direction_value, #flip direction for ratios
    discrete=TRUE,
    name=measure_value, #legend title
    na.value="grey")+
  #  theme_classic()+
  theme_minimal()+
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )+
  facet_grid(
    cols=vars(scenario_intervention)
  )
}

gg_irr_pb=zcta_ca_geo_simplified %>% 
  left_join(irr_long, by = "zcta") %>% 
  filter(scenario_type_3 =="Population-based") %>% 
  ggplot_facet_pb_imp_v_tree(measure_value="IRR",direction_value=-1)

gg_irr_pb
```


### Proportionate Universalism and Targeted Scenarios
#### Impervious Surfaces

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
ggplot_facet_each_int_type=function(df, measure_value, direction_value){
  df %>% 
  filter(scenario_type_3 !="Population-based") %>% #excluding these
  ggplot()+
  geom_sf(
    aes(fill=value_cat),
    linewidth=.05)+
  scale_fill_viridis(
    direction=direction_value, #flip direction for ratios
    discrete=TRUE,
    name=measure_value, #legend title
    na.value="grey")+
#  theme_classic()+
  theme_minimal()+
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
    )+
  facet_grid(
    cols=vars(scenario_sub_type),
    rows=vars(scenario_type_3)
  )
  
}

zcta_ca_geo_simplified %>% 
  left_join(irr_long, by = "zcta") %>% 
  filter(scenario_intervention=="Imp") %>% 
  ggplot_facet_each_int_type(measure_value="IRR",direction_value=-1)


```

#### Tree canopy

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
zcta_ca_geo_simplified %>% 
  left_join(irr_long, by = "zcta") %>% 
  filter(scenario_intervention=="Tree") %>% 
  ggplot_facet_each_int_type(measure_value="IRR",direction_value=-1)
```

## IRD

### Population-based scenarios: Impervious surfaces vs. Tree canopy

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
zcta_ca_geo_simplified %>% 
  left_join(ird_long, by = "zcta") %>% 
  filter(scenario_type_3 =="Population-based") %>% 
  ggplot_facet_pb_imp_v_tree(measure_value="IRD",direction_value=1)
```

#### Impervious surfaces

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
zcta_ca_geo_simplified %>% 
  left_join(ird_long, by = "zcta") %>% 
  filter(scenario_intervention=="Imp") %>% 
  ggplot_facet_each_int_type(measure_value="IRD",direction_value=1)
```

#### Tree canopy
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
zcta_ca_geo_simplified %>% 
  left_join(ird_long, by = "zcta") %>% 
  filter(scenario_intervention=="Tree") %>% 
  ggplot_facet_each_int_type(measure_value="IRD",direction_value=1)
```


## Difference, number of cases

### Population-based scenarios: Impervious surfaces vs. Tree canopy

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
names(n_cases_diff_long)
zcta_ca_geo_simplified %>% 
  left_join(n_cases_diff_long, by = "zcta") %>% 
  filter(scenario_type_3 =="Population-based") %>% 
  ggplot_facet_pb_imp_v_tree(measure_value="n_cases_diff",direction_value=1)
```

#### Impervious surfaces

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
zcta_ca_geo_simplified %>% 
  left_join(n_cases_diff_long, by = "zcta") %>% 
  filter(scenario_intervention=="Imp") %>% 
  ggplot_facet_each_int_type(measure_value="n_cases_diff",direction_value=1)
```

#### Tree canopy
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
zcta_ca_geo_simplified %>% 
  left_join(n_cases_diff_long, by = "zcta") %>% 
  filter(scenario_intervention=="Tree") %>% 
  ggplot_facet_each_int_type(measure_value="n_cases_diff",direction_value=1)
```

