---
title: "Hospitalization scenarios"
#author: "Michael Garber"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc_float: true
---

```{r}
#| echo: false
#| warning: false
#Load data and packages
#Feb 13 2022 update using long-form data.
#Revising Dec 10, 2024
library(here)
library(mapview) #make sure mapview is github version
library(tidyverse)
library(viridis)
library(viridisLite)
library(leaflet)
library(leaflet.extras)
library(tmap)
source(here("scripts","read-attrib-hosps-ratios-diffs.R"))#load measures
setwd(here("data-processed"))
load("zcta_ca_geo_simplified.RData")


#Data created here:
#heat-hosp-california/scripts/link-zcta-hosp-data.R
```


# Scenario definitions

-   Tree canopy

    -   Population-based Scenario: AI: Increase by 10% in all zip codes

    -   Targeted

        -   Scenario AII1: Increase by 10% in zip codes in the lowest 1/5th of current TC cover (i.e. \<=20th pctile)

        -   Scenario AII2: Increase by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. \>80th pctile)

        -   Scenario AII3: Increase by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. \>80th pctile)

    -   Proportionate-universalism

        -   Scenario AIII1: Increase by 10% for bottom 1/5th of current TC cover... down to 2% for top 1/5th

        -   Scenario AIII2: Increase by 10% for top 1/5th of SVI ... down to 2% for bottom 1/5th

        -   Scenario AIII3: Increase by 10% for top 1/5th of hospitalization burden ... down to 2% for bottom 1/5th

-   Impervious surface cover

    -   Population-based: Scenario BI: Decrease by 10% in all zip codes

    -   Targeted

        -   Scenario BII1: Decrease by 10% in zip codes in the highest 1/5th of current imperv cover (i.e. \>80th pctile)

        -   Scenario BII2: Decrease by 10% in zip codes in the highest 1/5th of the Social Vulnerability Index (i.e. \>80th pctile)

        -   Scenario BII3: Decrease by 10% in zip codes in the highest 1/5th of hospitalization burden (i.e. \>80th pctile)

    -   Proportionate-universalism

        -   Scenario BIII1: Decrease by 10% for top 1/5th of current imperv cover ... down to 2% for bottom 1/5th

        -   Scenario BIII2: Decrease by 10% for top 1/5th of SVI ... down to 2% for bottom 1/5th

        -   Scenario BIII3: Decrease by 10% for top 1/5th of hospitalization burden ... down to 2% for bottom 1/5th



# Data check
Number of zip codes with scenarios by scenario type
```{r}
#| echo: false
#| warning: false
library(knitr)
hosp_all_long %>% 
  filter(measure=="irr") %>% 
  group_by(scenario_intervention,scenario_type_7_abbrev) %>% 
  summarise(n_scenario=n()) %>% 
  ungroup() %>% 
  kable(digits=4)
```

Implausible or unusual data
Are there zip codes with ratios above 2?
This implies the counterfactual scenario has twice as many cases as baseline
```{r}
#| echo: false
#| warning: false

n_by_scenario=hosp_all_long %>% 
   filter(measure=="irr") %>% 
  group_by(scenario_intervention,scenario_type_7_abbrev) %>% 
  summarise(n_scenario=n())


hosp_all_long %>% 
  filter(measure=="irr") %>%
  filter(value>2) %>% 
  group_by(scenario_intervention,
           scenario_type_3,scenario_sub_type, scenario_type_7_abbrev) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  left_join(n_by_scenario,by=c("scenario_intervention",
    "scenario_type_7_abbrev")) %>% 
  mutate(prop=n/n_scenario) %>% 
  kable(digits=4)

```

Ratios below zero? This implies the counterfactual scenario yields a negative number
(negative predicted hospitalizations)
```{r}
#| echo: false
#| warning: false
hosp_all_long %>% 
  filter(measure=="irr") %>%
  filter(value<0) %>% 
  group_by(scenario_intervention,
           scenario_type_3,scenario_sub_type, scenario_type_7_abbrev) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
    left_join(n_by_scenario,by=c("scenario_intervention",
    "scenario_type_7_abbrev")) %>% 
  mutate(prop=n/n_scenario)%>% 
  kable(digits=4)
```



# Plots
## Histograms of IRR, IRD, and diff in n cases
Facet by type of intervention (impervious surfaces vs tree canopy) and by scenario type - Population-based, Proportionate Universalism, Targeted
```{r}
#| echo: false
#| warning: false
facet_histogram_fun=function(df){
  df %>% 
      ggplot(aes(value))+
      geom_histogram()+
      facet_grid(
        rows=vars(scenario_type_7_abbrev),
        cols=vars(scenario_intervention)
      )
}

#IRR
hosp_all_long %>% 
  filter(measure=="irr") %>%
  #Remove ratios above 2
  filter(value<2) %>%
  #remove negative ratios
  filter(value>0) %>% 
  facet_histogram_fun()+
  xlab("IRR")

#IRD
hosp_all_long %>% 
  filter(measure=="ird") %>%
  filter(value<1e-6) %>% #Exclude outliers
  facet_histogram_fun()+
  xlab("IRD")

#n cases
hosp_all_long %>% 
  filter(measure=="n_cases_diff") %>%
  facet_histogram_fun()+
  xlab("n_cases_diff")
```

## Bar charts

### Median IRR 
```{r}
#| echo: false
#| warning: false
hosp_all_long %>% 
  filter(measure=="irr") %>% 
  group_by(measure, scenario) %>% 
  summarise(irr_med=median(value,na.rm=TRUE)) %>% 
  ungroup() %>% 
  left_join(lookup_scenario, by ="scenario") %>% 
  ggplot(aes(y=irr_med,x=scenario_type_7_abbrev))+
  geom_col()+
  labs(x="Scenario", y="Median IRR over ZCTA")+
  facet_grid(
    #Move facet down to x-axis
    #https://stackoverflow.com/questions/67519146/bar-plot-with-named-groups-on-x-axis-in-ggplot2
    cols=vars(scenario_intervention),
    scales="free_x",
    space="free_x",
    switch="x"
  )+
  theme(panel.spacing = unit(0, units = "cm"), # removes space between panels
        strip.placement = "outside", # moves the states down
        strip.background = element_rect(fill = "white") 
  )

```

### Median IRD
```{r}
#| echo: false
#| warning: false
hosp_all_long %>% 
  filter(measure=="ird") %>% 
  group_by(measure, scenario) %>% 
  summarise(ird_med=median(value,na.rm=TRUE)) %>% 
  ungroup() %>% 
  left_join(lookup_scenario, by ="scenario") %>% 
  ggplot(aes(y=ird_med,x=scenario_type_7_abbrev))+
  geom_col()+
  labs(x="Scenario", y="Median IRD over ZCTA")+
  facet_grid(
    #Move facet down to x-axis
    #https://stackoverflow.com/questions/67519146/bar-plot-with-named-groups-on-x-axis-in-ggplot2
    cols=vars(scenario_intervention),
    scales="free_x",
    space="free_x",
    switch="x"
  )+
  theme(panel.spacing = unit(0, units = "cm"), # removes space between panels
        strip.placement = "outside", # moves the states down
        strip.background = element_rect(fill = "white") 
  )

```

### Median n_cases_diff
```{r}
#| echo: false
#| warning: false
hosp_all_long %>% 
  filter(measure=="n_cases_diff") %>% 
  group_by(measure, scenario) %>% 
  summarise(n_cases_diff_med=median(value,na.rm=TRUE)) %>% 
  ungroup() %>% 
  left_join(lookup_scenario, by ="scenario") %>% 
  ggplot(aes(y=n_cases_diff_med,x=scenario_type_7_abbrev))+
  geom_col()+
  labs(x="Scenario", y="Median diff. in N cases over ZCTA")+
  facet_grid(
    #Move facet down to x-axis
    #https://stackoverflow.com/questions/67519146/bar-plot-with-named-groups-on-x-axis-in-ggplot2
    cols=vars(scenario_intervention),
    scales="free_x",
    space="free_x",
    switch="x"
  )+
  theme(panel.spacing = unit(0, units = "cm"), # removes space between panels
        strip.placement = "outside", # moves the states down
        strip.background = element_rect(fill = "white") 
  )

```

### Total n_cases_diff
```{r}
#| echo: false
#| warning: false
hosp_all_long %>% 
  filter(measure=="n_cases_diff") %>% 
  group_by(measure, scenario) %>% 
  summarise(n_cases_diff_sum=sum(value,na.rm=TRUE)) %>% 
  ungroup() %>% 
  left_join(lookup_scenario, by ="scenario") %>% 
  ggplot(aes(y=n_cases_diff_sum,x=scenario_type_7_abbrev))+
  geom_col()+
  labs(x="Scenario", y="Sum diff. in N cases over ZCTA")+
  facet_grid(
    #Move facet down to x-axis
    #https://stackoverflow.com/questions/67519146/bar-plot-with-named-groups-on-x-axis-in-ggplot2
    cols=vars(scenario_intervention),
    scales="free_x",
    space="free_x",
    switch="x"
  )+
  theme(panel.spacing = unit(0, units = "cm"), # removes space between panels
        strip.placement = "outside", # moves the states down
        strip.background = element_rect(fill = "white") 
  )

```


